### 2023-05-18 manuscript.tex
Merge remote-tracking branch 'origin/main' [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/55b211690e436edabc36739a1bca1546f2b6d680.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/55b211690e436edabc36739a1bca1546f2b6d680/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5014914749

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/0e5545c8430c3f287c3b3a8c7618cf039d63b9d9/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/0e5545c8430c3f287c3b3a8c7618cf039d63b9d9}{stain/2022-fdo-paper@0e5545c}
on May 18, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/55b211690e436edabc36739a1bca1546f2b6d680/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/55b211690e436edabc36739a1bca1546f2b6d680}{stain/2022-fdo-paper@55b2116}
on May 18, 2023.
